---
title: "Visualizing plant-hummingbird meta-networks"
output: html_document
knit: (function(inputFile, encoding) {
      out_dir <- "knitted_markdown_files";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
---

**Goal**

Visualize overall network of plant-hummingbird interactions for this study system, across all sites and years studied, for each sampling method (pollen and camera)

These interactions can be thought of 'normal' visitation patterns, unmanipulated by the Heliconia removal experiment, because the data used are only from the 'pre' period.

```{r setup, include = FALSE}
library(tidyr)
library(dplyr)
library(bipartite)
```

## Step 1: Get data

These datasets have already been summarized in scripts 01-02

**Pollen data**
```{r step1a}
#Rename Heliconia genus. Will hide all other plant species in the visualization, becaues the morphotype names will not mean much to anyone else
pollen_data <- read.csv("../data/export/for_analysis/Pollen_data_summarized_for_metanetwork.csv") %>%
  select(bird_scientific_name, pollen_morphotype, num_slides) %>%
  mutate(pollen_morphotype = ifelse(pollen_morphotype == "HELICONIA01", "Heliconia", pollen_morphotype))

#How many different pollen morphotypes? Note: this is lower than the total number detected ever (N = 45), because it excludes some of the data
unique(pollen_data$pollen_morphotype) %>% length()

#How many different bird species?
unique(pollen_data$bird_scientific_name) %>% length()

#Create matrix
pollen_data_wide <- pollen_data %>%
   pivot_wider(names_from = bird_scientific_name, values_from = num_slides, values_fill = list(num_slides = 0))

pollen_matrix <- data.matrix(pollen_data_wide)[,-1]
rownames(pollen_matrix) <- as.character(pollen_data_wide$pollen_morphotype)
```

**Camera data**
```{r step1b}
camera_data <- read.csv("../data/export/for_analysis/Camera_data_summarized_for_metanetwork.csv") %>%
  select(bird_scientific_name, plant_scientific_name, sightings_per_hour) %>%
  mutate(plant_scientific_name = ifelse(plant_scientific_name == "Drymonia sp.", "Drymonia", plant_scientific_name)) %>% 
  mutate(plant_scientific_name = ifelse(plant_scientific_name == "Renealmia sp.", "Renealmia", plant_scientific_name)) %>% 
  mutate(plant_scientific_name = ifelse(plant_scientific_name == "Heliconia tortuosa", "Heliconia", plant_scientific_name)) 

#What species had no visitation?
species_with_no_visits <- camera_data %>%
  group_by(plant_scientific_name) %>%
  summarise(max_rate = max(sightings_per_hour)) %>%
  filter(max_rate == 0)

#Remove these species
camera_data_with_visits <- camera_data %>%
  filter(!plant_scientific_name %in% species_with_no_visits$plant_scientific_name)
  
#How many different bird species?
unique(camera_data_with_visits$bird_scientific_name) %>% length()

#How many different plant species with visits?
unique(camera_data_with_visits$plant_scientific_name) %>% length()

#Create matrix
camera_data_wide <- camera_data_with_visits %>%
  pivot_wider(names_from = bird_scientific_name, values_from = sightings_per_hour, values_fill = list(sightings_per_hour = 0))

camera_matrix <- data.matrix(camera_data_wide)[,-1]
rownames(camera_matrix) <- as.character(camera_data_wide$plant_scientific_name)
```

## Step 2: Visualize pollen metanetwork
```{r step2, fig.width=12, fig.height=10, results = 'hide'}
#Highlight color 
red = "#BA0022"

#Italics
graphics::par(font = 3)

#1. Hide all labels except Heliconia by making them white
#2. Emphasize green hermit and violet sabrewing
#3. Emphasize Heliconia (highlight in red)

bipartite::plotweb(pollen_matrix, method = "cca", arrow = "no",
                   text.rot = 90, labsize = 2,
                   text.low.col = ifelse(rownames(pollen_matrix) == "Heliconia", "black", "white"),
                   text.high.col = ifelse(colnames(pollen_matrix) == "Phaethornis guy" | colnames(pollen_matrix) == "Campylopterus hemileucurus", "black", "grey40"),
                   y.lim = c(-0.75, 2.75),
                   x.lim = c(0, 1.75),
                   col.low = ifelse(rownames(pollen_matrix) == "Heliconia", red, "grey10"),
                   bor.col.low = NA,
                   col.interaction = t(ifelse(pollen_matrix[,] > 0 & rownames(pollen_matrix) == "Heliconia", red, "grey80")),
                   bor.col.interaction = t(ifelse(pollen_matrix[,] > 0 & rownames(pollen_matrix) == "Heliconia", red, "black")))

pollen_network <- grDevices::recordPlot()
png("../results/network_visualizations/metanetworks/Pollen_metanetwork.png", width = 12, height = 10, res = 300, units = "in", bg = "white")
pollen_network
dev.off()
```

## Step 3: Visualize camera metanetwork
```{r step3, fig.width=12, fig.height=10, results = 'hide'}
#Italics
graphics::par(font = 3)

#1. Hide all labels except Heliconia by making them white
#2. Emphasize green hermit and violet sabrewing
#3. Emphasize Heliconia (highlight in red)
bipartite::plotweb(camera_matrix, method = "cca", arrow = "no",
                   text.rot = 90, labsize = 2,
                   text.low.col = ifelse(rownames(camera_matrix) == "Heliconia", "black", "white"),
                   text.high.col = ifelse(colnames(camera_matrix) == "Phaethornis guy" | colnames(camera_matrix) == "Campylopterus hemileucurus", "black", "grey40"),
                   y.lim = c(-0.75, 2.75),
                   x.lim = c(0, 1.75),
                   col.low = ifelse(rownames(camera_matrix) == "Heliconia", red, "grey10"),
                   bor.col.low = NA,
                   col.interaction = t(ifelse(camera_matrix[,] > 0 & rownames(camera_matrix) == "Heliconia", red, "grey80")),
                   bor.col.interaction = t(ifelse(camera_matrix[,] > 0 & rownames(camera_matrix) == "Heliconia", red, "black")))

camera_network <- grDevices::recordPlot()
png("../results/network_visualizations/metanetworks/Camera_metanetwork.png", width = 12, height = 10, res = 300, units = "in", bg = "white")
camera_network
dev.off()
```

## Step 4: Combine plots and export
```{r}
network_multiplot <- ggpubr::ggarrange(camera_network, pollen_network, ncol = 1, align = "h")

ggplot2::ggsave("../results/network_visualizations/metanetworks/Pollen_and_camera_metanetworks_multiplot.png", network_multiplot, width = 10, height = 18, dpi = 300, units = "in", bg = "white")
```

