---
title: "Making toy networks for turnover figure"
output: html_document
knit: (function(inputFile, encoding) {
      out_dir <- "knitted_markdown_files";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
---

**Goal**

Make demo networks to help communicate each component of network dissimilarity (total, species turnover, and 'rewiring')

```{r setup, include = FALSE}
library(vegan)
library(dplyr)
library(tidyr)
library(bipartite)

```

## Step 1: Make up some data
```{r}
#Want to have 3 plants and 3 birds
before <- data.frame(plant_species = c("plant1", "plant2", "plant3"), bird1 = c(1, 1, 0), bird2 = c(1, 0, 1), bird3 = c(1, 0, 0))
after <- data.frame(plant_species = c("plant1", "plant2", "plant3"), bird1 = c(0, 1, 1), bird2 = c(1, 0, 1), bird4 = c(0, 1, 1))

#Matrices
before_matrix <- data.matrix(before)[,-1] #Get rid of first column
rownames(before_matrix) <- before$plant_species
before_matrix

after_matrix <- data.matrix(after)[,-1] #Get rid of first column
rownames(after_matrix) <- after$plant_species
after_matrix

#Combine networks so I can highlight what was gained/lost
#If the partners interacted **at any point** (before or after), include that here
before_and_after <- bind_rows(before, after) %>%
  pivot_longer(cols = c(bird1, bird2, bird3, bird4), names_to = "bird_species") %>%
  mutate(bird_plant = paste(bird_species, plant_species, sep = "_")) %>%
  filter(value > 0) %>%
  filter(!is.na(value)) %>%
  distinct()

before_and_after_wide <- before_and_after %>%
  select(-bird_plant) %>%
  pivot_wider(names_from = bird_species, values_from = value, values_fill = 0)

#Convert to matrix
before_and_after_matrix <- data.matrix(before_and_after_wide)[,-1] #Get rid of first column
rownames(before_and_after_matrix) <- before_and_after_wide$plant_species
before_and_after_matrix
```

How many interactions in each network?
```{r}
#Total number of interactions per network
#multiply total # species in network by # links/species
(networklevel(before_matrix, index = "number of species")[[1]] + networklevel(before_matrix, index = "number of species")[[2]]) * networklevel(before_matrix, index = "links per species")[[1]]
(networklevel(after_matrix, index = "number of species")[[1]] + networklevel(after_matrix, index = "number of species")[[2]]) * networklevel(after_matrix, index = "links per species")[[1]]
```

## Step 2: Visualize before and after networks in black and white (no color coding)
```{r}
plotweb(before_matrix, method = "normal", arrow = "no", low.lablength = 0, high.lablength = 0) 

network_before <- recordPlot() #from package grDevices
png("../results/network_visualizations/toy_networks/Toy_network_before_bw.png", width = 12, height = 10, res = 300, units = "in")
network_before
dev.off()

plotweb(after_matrix, method = "normal", arrow = "no", low.lablength = 0, high.lablength = 0)
network_after <- recordPlot() #from package grDevices
png("../results/network_visualizations/toy_networks/Toy_network_after_bw.png", width = 12, height = 10, res = 300, units = "in")
network_after
dev.off()

plotweb(before_and_after_matrix, method = "normal", arrow = "no")
```

## Step 3: Color-code interactions by component (species turnover vs. rewiring) and type (interaction gain vs. interaction loss)

Code interactions by type
```{r}
#2 = interaction loss (species turnover)
#3 = interaction gain (species turnover)
#4 = interaction loss (rewiring)
#5 = interaction gain (rewiring)

before_and_after_coded <- before_and_after %>%
  mutate(value = ifelse(bird_species == "bird3", 2, value)) %>%
  mutate(value = ifelse(bird_species == "bird4", 3, value)) %>%
  mutate(value = ifelse(bird_plant == "bird1_plant1", 4, value)) %>%
  mutate(value = ifelse(bird_plant == "bird1_plant3", 5, value))

before_and_after_coded_wide <- before_and_after_coded %>%
  select(-bird_plant) %>%
  pivot_wider(names_from = bird_species, values_from = value, values_fill = 0)

before_and_after_matrix_coded <- data.matrix(before_and_after_coded_wide)[,-1] #Get rid of first column
rownames(before_and_after_matrix_coded) <- before_and_after_coded_wide$plant_species
before_and_after_matrix_coded
```

Calculate betalink metrics for these networks
```{r}
webs_array <- webs2array(list(before_matrix, after_matrix))
betalink <- betalinkr(webs_array, partitioning = "commondenom", index = "bray", partition.st = TRUE, partition.rr = FALSE, binary = TRUE)

betalink_df <- as.data.frame(t(betalink))
betalink_df

#Check to make sure components were calculated correctly
betalink_df$WN
betalink_df$ST + betalink_df$OS
```

Highlight interactions that were lost/gained
```{r}
colors <- c("#6D80EB", "#0E0D37", "#E06F81", "#BA0022") #light blue, dark blue, light red, dark red

matrix_binary = before_and_after_matrix
matrix_coded = before_and_after_matrix_coded

#Blue = rewiring, Red = gain/loss
plotweb(matrix_binary, method="normal", arrow="no",
        low.lablength=0, high.lablength=0,
        col.interaction = t(ifelse(matrix_coded[,] == 2, adjustcolor(colors[[1]], alpha.f = 1), #loss (species turnover)
                                   ifelse(matrix_coded[,] == 3,  adjustcolor(colors[[2]], alpha.f = 1), #gain (species turnover)
                                          ifelse(matrix_coded[,] == 4,  adjustcolor(colors[[3]], alpha.f = 1), #loss (rewiring)
                                                 ifelse(matrix_coded[,] == 5,  adjustcolor(colors[[4]], alpha.f = 1), "grey80")))))) #gain (rewiring)


network_WN <- recordPlot() #from package grDevices
png("../results/network_visualizations/toy_networks/Toy_network_WN_color_coded.png", width = 12, height = 10, res = 300, units = "in")
network_WN
dev.off()
```

Highlight interactions that were lost/gained due to species turnover only
```{r}
plotweb(matrix_binary, method="normal", arrow="no",
        low.lablength=0, high.lablength=0,
        col.interaction = t(ifelse(matrix_coded[,] == 2, adjustcolor(colors[[1]], alpha.f = 1), #loss (species turnover)
                                   ifelse(matrix_coded[,] == 3,  adjustcolor(colors[[2]], alpha.f = 1), "grey80")))) #gain (species turnover)

network_ST <- recordPlot() #from package grDevices
png("../results/network_visualizations/toy_networks/Toy_network_ST_color_coded.png", width = 12, height = 10, res = 300, units = "in")
network_ST
dev.off()
```

Highlight interactions that were lost/gained due to rewiring
```{r}
plotweb(matrix_binary, method="normal", arrow="no",
        low.lablength=0, high.lablength=0,
        col.interaction = t(ifelse(matrix_coded[,] == 4, adjustcolor(colors[[3]], alpha.f = 1), #loss (rewiring)
                                   ifelse(matrix_coded[,] == 5,  adjustcolor(colors[[4]], alpha.f = 1), "grey80")))) #gain (rewiring)
 
network_OS <- recordPlot() #from package grDevices
png("../results/network_visualizations/toy_networks/Toy_network_OS_color_coded.png", width = 12, height = 10, res = 300, units = "in")
network_OS
dev.off()
```

